Constraining the High Density Nuclear Symmetry Energy with Pions

### 2020-05-30 chapters/ch_data_analysis_2.tex
Update analysis section

\section{Beam Particle Identification}
Figures of beam contaminants in our beam PID line. 
Table of beam purity reference to Jon's thesis paper

Beam tracking was handled by the BigRIPS spectrometer tracking system. Each individual beam particles coming down the spectrometer was measured using a dE-Time-of-Flight method where the charge, Z, and mass to charge ratio, A/Q, of each particle was measured. Individual particle species represent a two-dimensional Gaussian in this space; both the $\tin{132}{112}$ and $\tin{108}{124}$ systems are shown in Fig.~\ref{fig:beampid}. Clear separation is seen for each particle species and the correct value of Z and A/Q gives us the correct species type. Each species of interest is fitted with multivariate normal distribution with two variables defined as,

@@

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{beamAngle-Sn108.png} 
        \caption{Generic} \label{fig:beamangle108}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{beamAngle-Sn112.png} 
        \caption{Competitors} \label{fig:beamangle112}
    \end{subfigure}

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{beamAngle-Sn124.png} 
        \caption{Generic} \label{fig:beamangle124}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{beamAngle-Sn132.png} 
        \caption{Competitors} \label{fig:beamangle132}
    \end{subfigure}
\label{fig:beamangle}
\end{figure}

>>>>

\section{Beam Particle Identification}
%Figures of beam contaminants in our beam PID line. 
%Table of beam purity reference to Jon's thesis paper

Each beam  was tracked by the BigRIPS spectrometer tracking system as it traveled down the beam pipe using the dE-Time-of-Flight method where the charge, Z, and mass to charge ratio, A/Q, of each particle was measured. Individual particle species represent a two-dimensional Gaussian in this space; both the $\tin{132}{112}$ and $\tin{108}{124}$ systems are shown in Fig.~\ref{fig:beampid}. Clear separation is seen for each particle species and the correct value of Z and A/Q gives us the correct species type. Each species of interest is fitted with multivariate normal distribution with two variables defined as,

@@

\begin{figure}[!htb]
    \centering
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{beamAngle-Sn108.png} 
        \caption{Beam angle of the $\tin{108}{124}$ system} \label{fig:beamangle108}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{beamAngle-Sn112.png} 
        \caption{Beam angle of the $\tin{112}{124}$ system} \label{fig:beamangle112}
    \end{subfigure}

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{beamAngle-Sn124.png} 
        \caption{Beam angle of the $\tin{124}{112}$ system} \label{fig:beamangle124}
    \end{subfigure}
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{beamAngle-Sn132.png} 
        \caption{Beam angle of the $\tin{132}{124}$ system} \label{fig:beamangle132}
    \end{subfigure}
\label{fig:beamangle}
\end{figure}
